Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
adding boxplots and cleaning
last updates

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code in the best ranked files. Table \ref{tab:red} shows, as
percentages, the reduction of the top file sizes
obtained with dynamic slicing for different values of
$k$. Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files. \Mar{sofia, it would be more convincing if you (additionally)
  show reduction wrt to the the parts of the file that are covered.}

@@

A fundamental issue of purely dynamic slicing techniques is the risk
of discarding faulty statements (see Section~\ref{sec:slicing}). This
research question evaluates the practical impact of this conceptual
issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
dynamic slicing captures at least one of the faulty statements among
the sliced files for different values of $k$. These numbers indicat
that \Fix{...elaborate...}

@@

        \lang{}            & 100.0 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

@@

>>>>

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code in the best ranked files. Table \ref{tab:red} shows, as
percentages, the reduction of the top file sizes
obtained with dynamic slicing for different values of
$k$. Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files.

%\Mar{sofia, it would be more convincing if you (additionally)
%  show reduction wrt to the the parts of the file that are covered.}

@@

A fundamental issue of purely dynamic slicing techniques is the risk
of discarding faulty statements (see Section~\ref{sec:slicing}). This
research question evaluates the practical impact of this conceptual
issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
dynamic slicing captures at least one of the faulty statements among
the sliced files for different values of $k$. These numbers indicate
that in general \ds{} finds at least one faulty statement in the top
$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
is slightly improved for $91.2\%$ if we consider 
the top $10$ of the highest-ranked faulty classes.
\Sof{Percebo o objectivo da tabela 3 mas não seria melhor arranjar 
maneira de não precisar de repetir? Estes resultados estão na tabela 4}

@@

        \lang{}            & 100.0 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\\midrule
        Total          & 87.3 & 91.2\\

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot_>0.pdf}
		\caption{Boxplot of $\Delta{}C$. \Sof{Considering only the best cases}}
		\label{fig:boxplot}
\end{figure}

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
		\label{fig:boxplot}
\end{figure}
